Prevalence, ANC, ART model inference case-study

### 2023-06-22 src/docs_15-11-22-seminar/15-11-22-seminar.Rmd
Work on slides for HIV Lab Group #25
Replace all elgm-inf with naomi-aghq

\begin{center}
\begin{tcolorbox}[width=0.9\textwidth, colframe={title}, colback={white}, title={}]
Notebook for this example at \texttt{athowes.github.io/elgm-inf/epil}
\end{tcolorbox}
\end{center}

@@

\begin{center}
\begin{tcolorbox}[width=0.9\textwidth, colframe={title}, colback={white}, title={}]
Notebook for this example at \texttt{athowes.github.io/elgm-inf/prev-anc-art}
\end{tcolorbox}
\end{center}

@@

* Joint work with Alex Stringer (Waterloo) and my PhD supervisors Seth Flaxman (Oxford) and Jeff Eaton (Imperial)
* The code for this project is at `github.com/athowes/elgm-inf`
* You can find me online at `athowes.github.io`

>>>>

\begin{center}
\begin{tcolorbox}[width=0.9\textwidth, colframe={title}, colback={white}, title={}]
Notebook for this example at \texttt{athowes.github.io/naomi-aghq/epil}
\end{tcolorbox}
\end{center}

@@

\begin{center}
\begin{tcolorbox}[width=0.9\textwidth, colframe={title}, colback={white}, title={}]
Notebook for this example at \texttt{athowes.github.io/naomi-aghq/prev-anc-art}
\end{tcolorbox}
\end{center}

@@

* Joint work with Alex Stringer (Waterloo) and my PhD supervisors Seth Flaxman (Oxford) and Jeff Eaton (Imperial)
* The code for this project is at `github.com/athowes/naomi-aghq`
* You can find me online at `athowes.github.io`

### 2023-06-22 src/docs_18-04-23-lab-group/18-04-23-lab-group.Rmd
Replace all elgm-inf with naomi-aghq

* Working on a paper based on this work called "Fast approximate Bayesian inference for small-area estimation of HIV indicators using the Naomi model" joint with Alex Stringer (Waterloo), Seth Flaxman (Oxford), Jeff Eaton (Imperial)
* Code and notebooks for this project are available at `athowes.github.io/elgm-inf`

>>>>

* Working on a paper based on this work called "Fast approximate Bayesian inference for small-area estimation of HIV indicators using the Naomi model" joint with Alex Stringer (Waterloo), Seth Flaxman (Oxford), Jeff Eaton (Imperial)
* Code and notebooks for this project are available at `athowes.github.io/naomi-aghq`

### 2023-06-22 src/docs_21-06-23-mlgh/21-06-23-mlgh.Rmd
Replace all elgm-inf with naomi-aghq

<!-- https://github.com/athowes/elgm-inf/blob/fd4b0bb6b9ba93ac277de7aad47a94581e8fc900/src/docs_18-04-23-explainer/18-04-23-explainer.Rmd -->

@@

* Code and notebooks: `github.com/athowes/elgm-inf`
* Working paper on the way^[For sufficiently vague definition of "on the way"], Any early readers greatly appreciated!
  * Fast approximate Bayesian inference for small-area estimation of HIV indicators using the Naomi model $\color{lolit}{\text{Adam Howes, Alex Stringer, Seth Flaxman, Jeff Eaton}}$

@@

```{r, echo=FALSE, fig.cap="Custom version of Laplace marginals implemented using \\texttt{TMB}. Speed-up possible using Simon Wood's method? For the Epilepsy example from Rue (2009), see \\texttt{athowes/elgm-inf/src/epil}.", out.width = '60%'}
knitr::include_graphics("laplace.png")
```

>>>>

<!-- https://github.com/athowes/naomi-aghq/blob/fd4b0bb6b9ba93ac277de7aad47a94581e8fc900/src/docs_18-04-23-explainer/18-04-23-explainer.Rmd -->

@@

* Code and notebooks: `github.com/athowes/naomi-aghq`
* Working paper on the way^[For sufficiently vague definition of "on the way"], Any early readers greatly appreciated!
  * Fast approximate Bayesian inference for small-area estimation of HIV indicators using the Naomi model $\color{lolit}{\text{Adam Howes, Alex Stringer, Seth Flaxman, Jeff Eaton}}$

@@

```{r, echo=FALSE, fig.cap="Custom version of Laplace marginals implemented using \\texttt{TMB}. Speed-up possible using Simon Wood's method? For the Epilepsy example from Rue (2009), see \\texttt{athowes/naomi-aghq/src/epil}.", out.width = '60%'}
knitr::include_graphics("laplace.png")
```

### 2023-06-22 src/example_inla-replication/inla-replication.Rmd
Replace all elgm-inf with naomi-aghq

Under this approach, all weights would be equal $\Delta_k = 1 / K$.
For a more detailed run through of the grid integration method, see the [INLA two dimensional grid replication](https://athowes.github.io/elgm-inf/inla-grid.html) notebook.

>>>>

Under this approach, all weights would be equal $\Delta_k = 1 / K$.
For a more detailed run through of the grid integration method, see the [INLA two dimensional grid replication](https://athowes.github.io/naomi-aghq/inla-grid.html) notebook.

### 2023-06-22 src/prev-anc-art_results/prev-anc-art.Rmd
Slides up!
Replace all elgm-inf with naomi-aghq

| Model | Report | Components |
|:------|:-------|:-----------|
| 0 | [`prev-anc-art_model0`](https://github.com/athowes/elgm-inf/tree/master/src/prev-anc-art_model0) | Prevalence (no random effects) |
| 1 | [`prev-anc-art_model1`](https://github.com/athowes/elgm-inf/tree/master/src/prev-anc-art_model1) | Prevalence |
| 2 | [`prev-anc-art_model2`](https://github.com/athowes/elgm-inf/tree/master/src/prev-anc-art_model2) | Prevalence, ANC |
| 3 | [`prev-anc-art_model3`](https://github.com/athowes/elgm-inf/tree/master/src/prev-anc-art_model3) | Prevalence, ART |
| 4 | [`prev-anc-art_model4`](https://github.com/athowes/elgm-inf/tree/master/src/prev-anc-art_model4) | Prevalence, ANC, ART |

We perform inference on simulated data from Model 4 generated ([`prev-anc-art_sim`](https://github.com/athowes/elgm-inf/tree/master/src/prev-anc-art_sim)) with the following parameter values:

@@

```{r fig.height=8}
draw_ksplots_D(model4) + labs(title = "Model 4")
```

>>>>

| Model | Report | Components |
|:------|:-------|:-----------|
| 0 | [`prev-anc-art_model0`](https://github.com/athowes/naomi-aghq/tree/master/src/prev-anc-art_model0) | Prevalence (no random effects) |
| 1 | [`prev-anc-art_model1`](https://github.com/athowes/naomi-aghq/tree/master/src/prev-anc-art_model1) | Prevalence |
| 2 | [`prev-anc-art_model2`](https://github.com/athowes/naomi-aghq/tree/master/src/prev-anc-art_model2) | Prevalence, ANC |
| 3 | [`prev-anc-art_model3`](https://github.com/athowes/naomi-aghq/tree/master/src/prev-anc-art_model3) | Prevalence, ART |
| 4 | [`prev-anc-art_model4`](https://github.com/athowes/naomi-aghq/tree/master/src/prev-anc-art_model4) | Prevalence, ANC, ART |

We perform inference on simulated data from Model 4 generated ([`prev-anc-art_sim`](https://github.com/athowes/naomi-aghq/tree/master/src/prev-anc-art_sim)) with the following parameter values:

@@

```{r fig.height=8}
draw_ksplots_D(model4) + labs(title = "Model 4")

ggsave("ks-example.pdf", draw_ksplots_D_params(model4, params = "phi_prev[5]"), h = 4, w = 6.25)
```
